Supporting Information : Understanding the nanoscale structure of hexagonal phase lyotropic liquid crystal membranes

### 2018-05-22 Ben_Manuscripts/structure_paper/supporting_information.tex
Modifications for paper

\documentclass{article}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage[margin=1in]{geometry}
\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}

@@

%  \noindent
%  \begingroup
%	\fontsize{14pt}{14pt}\selectfont
%	\textbf{Further details regarding monomer parameterization} 
%  \endgroup
  \section{Further details regarding monomer parameterization}\label{section:parameterization}

@@

  \begin{figure}
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{fig:monomer}
  \end{figure}

  \begin{figure}
	\centering
        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
	\caption{The groups used for radial distribution calculations. Red atoms are in the
		tails group. Green atoms are in the head group region. The blue atom is sodium. 
		}\label{fig:monomer_color_coded}
  \end{figure}

  \begin{figure}
        \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwiched.png}
                \caption{}\label{fig:sandwiched}
        \end{subfigure}
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{PD.png}
                \caption{}\label{fig:pd}
        \end{subfigure}
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{Tshaped.png}
                \caption{}\label{fig:tshaped}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwichedlayers.png}
                \caption{}\label{fig:sandwichedlayers}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offsetlayers.png}
                \caption{}\label{fig:offsetlayers}
        \end{subfigure}
        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
        (d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
        configuration }\label{fig:stacking}
  \end{figure}

  \begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
	\caption{When creating an initial configuration, the pore radius is defined based
	on the distance of the carbonyl carbon from the pore's central axis}
	\label{fig:pore_radius_illustration}
  \end{figure}

@@

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
		than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
                value for all our simulations in the main text.
f		%The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
		%pore spacing. We chose to use this value for all our simulations in the main
		%text.

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

	  \begin{figure}
		\centering
		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
		are the same.}~\label{fig:p2p_diagram}
	  \end{figure}

	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
  	  \begin{figure}[htp]
		\centering
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_39.png}\quad
			\vspace{-1.25em}
			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_41.png}\quad
			\vspace{-1.25em}
			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_45.png}
			\vspace{-1.25em}
			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
			\vspace{-1.25em}
			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_55.png}
			\vspace{-1.25em}
			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
		\end{subfigure}

@@

		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
		slightly larger than the equilibrated pore radius of the system simulated with
		an intial pore radius of 2.5 \AA. After being run through the full dry
		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
		agrees with the 2.5 \AA~configuration within error.

@@

	  \begin{figure}
	  \centering
          \includegraphics[width=\textwidth]{slit_pores.png}
	  \caption{A system that was built with an initial pore radius of 8
		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
		  aromatic ring of the head group are colored orange and all else is colored
		  cyan.}~\label{fig:slits}
	  \end{figure}

@@

	  We tested 3 different initial layer spacings, defined as the distance
	  between the planes of aromatic rings in each layer. Systems built with layers
	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
	  will focus the discussion here on systems built with layers stacked 10 \AA~
	  apart.

@@

	  \begin{figure}
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{When layers are initially stacked 10 \AA~apart and the system
                is equilibrated using the dry equlibration procedure, large vacuum gaps
		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
	  \end{figure}

@@

%  \noindent
%  \begingroup
%        \fontsize{14pt}{14pt}\selectfont
%	\textbf{Calculation of pore-to-pore spacing statistics}
%  \endgroup
  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}

  \vspace{1em} 
  We are interested in 5 pore-to-pore distances which should all be
  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
  the 5 distances are independent. We can calculate a trajectory of spacing
  versus time for each of the 5 distances. We calculated the average pore-to-pore
  spacing and its uncertainty according to the following procedure:
   \begin{enumerate}
	\item We calculated the time when each of the pore-to-pore distances
	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
	after the largest of the five values.
	\item We calculated how long it takes for the data in each of the 5
	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. 
	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
	five sub-trajectories of pore-to-pore spacings.   
	\item We generate statistics using the bootstrapping technique. For
	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
	sampling from the trajectory blocks. 
	\item The average pore-to-pore distance is the mean of all pore
	spacings among all bootstrap trials.
	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
	pore spacing for each pore over all bootstrap trials. Using the 5 average 
	pore-to-pore distances, we calculate the spread with:
	\begin{align}
	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
	\end{align}
	where $\overline{x}$ is the average pore-to-pore distance.
  \end{enumerate}

  \begin{figure}
	\centering
	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
	\caption{There are five pore-to-pore distances that are equal in a perfect
		hexagon. If each number in the diagram represents the center of a
		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
		are independent. For example, the distance from 1 to 4 is defined by
		the location of all other pore centers.}
	\label{fig:p2p_diagram}
  \end{figure}

%  \vspace{1em}
%  \begingroup
%	\fontsize{14pt}{12pt}\selectfont
%	\noindent \textbf{Experimental correlation length of R-$\pi$}\label{section:correlation_length}
%  \endgroup

  \subsubsection{\textit{The nematic order parameter}}\label{method:nematic_order}

  We calculated the nematic order parameter for our system in order to
  understand the degree of ordering among monomer head groups. Typically, the
  nematic order parameter is calculated for nematic liquid crystal systems which
  are characterized by unidirectional ordering of liquid crystal monomers. The
  preferred direction of monomers is defined by the unit director vector,
  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
  order parameter, $S$, is defined as:
  \begin{equation}
	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
	\label{eqn:nematic_order_parameter}
  \end{equation}
  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
  In a perfectly ordered system, the molecular axis should be aligned with
  $\mathbf{n}$ and give an order parameter of $S=1$. We are interested in
  quantifying the degree of monomer head group alignment between systems. We use
  Eq.~\ref{eqn:nematic_order_parameter} to accomplish this by defining
  $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
  the aromatic head groups.

@@

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit paramaters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on lorentzian parameters
  \begin{figure}[h]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

% BJC5 : Move this figure to supporting
  \begin{figure}
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disorderd Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}

>>>>

\documentclass[journal=jpcbfk,manusciprt=article]{achemso}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{subcaption}
%\usepackage[margin=1in]{geometry}\usepackage{amsmath} % or simply amstext
\usepackage{siunitx}
\usepackage{booktabs}
\usepackage[export]{adjustbox}
\newcommand{\angstrom}{\textup{\AA}}
\usepackage{cleveref}
\usepackage{booktabs}
\usepackage{gensymb}
\usepackage{float}
\usepackage{listings}
\usepackage{xr}

\SectionNumbersOn

\externaldocument[M-]{draft}

@@

  \section{Attempted Self-assembly}\label{section:self_assembly}

  We attempted self assembly of Na-GA3C11 monomers by using an isotropic configuration
  generated using Packmol (\cite{martinez_packmol:_2009}). The input file given to 
  Packmol is shown below.
  \lstset{language=bash}
  \begin{lstlisting}
  tolerance 2.0
  output packed.pdb
  filetype pdb
  structure monomer.pdb
  		number 400
  		inside box 0. 0. 0. 84.3 84.3 84.3
  end structure
  \end{lstlisting}

  We used the same number of monomers (400) that we used in all other simulations. 
  Since Packmol does not have the capability to create monoclinic boxes, we used a cubic
  box with a volume of 660 $nm^3$, 25 \% larger than those used to create ordered unit
  cells we studied.

  We use the nematic order paramter as defined in section~\ref{method:nematic_order} to 
  observe any progress towards an system ordering.

  %BJC: picture of isotropic box (before and after?)
  %BJC: plot of nematic order parameter vs. time

  \section{Further details regarding monomer parameterization}\label{section:parameterization}

@@

  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer.png}
	\caption{Atomistic representation of the monomer Na-GA3C11. White atoms
		represent hydrogen, cyan atoms represent carbon, red atoms represent oxygen and
		the blue atom is sodium.}\label{fig:monomer}
  \end{figure}

  \begin{figure}[!htb]
	\centering
        \includegraphics[width=0.9\textwidth]{monomer_color_coded.png}
	\caption{The groups used for radial distribution calculations. Red atoms are in the
		tails group. Green atoms are in the head group region. The blue atom is sodium. 
		}\label{fig:monomer_color_coded}
  \end{figure}

  \begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{monomer_dihedrals.png}
  \caption{We measured the autocorrelation functions of the dihedrals highlighted in
  black. We only included dihedrals associated with the outer tails in our calculation
  since the position of the center tail leads to fundamentally different interactions and
  dynamics.}\label{fig:dihedrals}
  \end{figure}

  \begin{figure}[!htb]
        \centering
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwiched.png}
                \caption{}\label{fig:sandwiched}
        \end{subfigure}
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{PD.png}
                \caption{}\label{fig:pd}
        \end{subfigure}
        \begin{subfigure}[b]{0.32\textwidth}
                \centering
                \includegraphics[width=\textwidth]{Tshaped.png}
                \caption{}\label{fig:tshaped}
        \end{subfigure}
        \vskip\baselineskip
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{sandwichedlayers.png}
                \caption{}\label{fig:sandwichedlayers}
        \end{subfigure}
        \begin{subfigure}[b]{0.475\textwidth}
                \centering
                \includegraphics[width=\textwidth]{offsetlayers.png}
                \caption{}\label{fig:offsetlayers}
        \end{subfigure}
        \caption{(a) Sandwiched benzene dimers stack 3.8 \angstrom~apart. (b) Parallel-Displaced benzene dimers stack
        3.4 \angstrom~vertically and 1.6 \angstrom~horizontally apart. (c) T-shaped benzene dimers stack 5.0 \angstrom~apart.
        (d) Two monomer layers stacked in the sandwiched configuration (e) Two monomer layers stacked in the parallel-displaced
        configuration }\label{fig:stacking}
  \end{figure}

  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.8\textwidth]{pore_radius_illustration.png}
	\caption{When creating an initial configuration, the pore radius is defined based
	on the distance of the carbonyl carbon from the pore's central axis}
	\label{fig:pore_radius_illustration}
  \end{figure}

  \section{Calculation of pore-to-pore spacing statistics}\label{section:p2p_stats}

 %BJC: is it really necessary to explain this if I release the code? I don't explain
 %any of the other stats I calculate.
  \vspace{1em} 
  We are interested in 5 pore-to-pore distances which should all be
  equal in a perfect hexagonal array (Figure~\ref{fig:p2p_diagram}). Only 4 of
  the 5 distances are independent. We can calculate a trajectory of spacing
  versus time for each of the 5 distances. We calculated the average pore-to-pore
  spacing and its uncertainty according to the following procedure:
   \begin{enumerate}
	\item We calculated the time when each of the pore-to-pore distances
	were equilibrated using \\ \texttt{pymbar.timeseries.detectEquilibration()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. We began calculations
	after the largest of the five values.
	\item We calculated how long it takes for the data in each of the 5
	trajectories to become uncorrelated using \texttt{pymbar.timeseries.integratedAutocorrelationTime()}
	\cite{chodera_simple_2016,shirts_statistically_2008}. 
	\item We broke the full equilibrated trajectory into blocks of length $\tau$, where
	$\tau$ is the maximum of the five autocorrelation times calculated. Each block contains
	five sub-trajectories of pore-to-pore spacings.   
	\item We generate statistics using the bootstrapping technique. For
	each bootstrap trial, we reconstruct an equilibrium trajectory by randomly
	sampling from the trajectory blocks. 
	\item The average pore-to-pore distance is the mean of all pore
	spacings among all bootstrap trials.
	\item To calculate the uncertainty in pore-to-pore distance, we calculate the average 
	pore spacing for each pore over all bootstrap trials. Using the 5 average 
	pore-to-pore distances, we calculate the spread with:
	\begin{equation}
	s = \sqrt{\frac{1}{4} \sum_{i=1}^5 (x_i - \overline{x})^2} 
	\label{equation:p2p_stats}
	\end{equation}
	where $\overline{x}$ is the average pore-to-pore distance. We divided the sum in 
	equation~\ref{equation:p2p_stats} by 4 since there are only 4 independent pore
	spacings.

@@

		\item 45 \AA~: A pore spacing of 45 \AA~is about 10 \% larger
		than the experimental value. This systems exhibits the smallest response to our 
 		equilibration procedure (Figure~\ref{fig:p2p_45}) and we chose to use this
        value for all our simulations in the main text.
        %The equilibrated pore spacing is 4.23 $\pm$ 0.03 nm.
		%The system maintains hexagonal symmetry and exhibits the lowest uncertainty in
		%pore spacing. We chose to use this value for all our simulations in the main
		%text.

@@

		\item 55 \AA~: We tested a pore spacing of 55 \AA~which is at
		a distance where monomers in each pore no longer intersect those of adjacent pores. Once
		the restraining potential reaches 56 KJ mol$^{-1}$ nm$^{-2}$, the pore spacing
		changes erratically until it begins to settle when the force constants are
		below 3 KJ mol$^{-1}$ nm$^{-2}$ (Figure~\ref{fig:p2p_55}). We reccomend
		avoiding a system such as this where vacuum gaps between pore columns are
		introduced unnecessarily. %The system equilibrates to a pore spacing of 4.27
%		$\pm$ 0.18 nm. The 1-2 pore spacing is the outlier in this case with a pore
 %               spacing of 3.99 \AA~ which distorts the hexagonal array.

@@

	  \begin{figure}[!htb]
		\centering
		\includegraphics[width=0.4\textwidth]{p2p_diagram.png}
		\caption{In a perfect hexagonal, there are 5 distances that should be exactly
		equal. As pictured in this diagram the distance from 1-2, 1-3, 1-4, 2-4, and 3-4
		are the same.}~\label{fig:p2p_diagram}
	  \end{figure}

	  %BJC: Could put vertical lines to indicate where position restraint values are reduced
  	  \begin{figure}[!htb]
		\centering
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_39.png}\quad
			\vspace{-1.25em}
			\caption{39 \AA~initial pore spacing}~\label{fig:p2p_39}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_41.png}\quad
			\vspace{-1.25em}
			\caption{41 \AA~initial pore spacing}~\label{fig:p2p_41}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_45.png}
			\vspace{-1.25em}
			\caption{45 \AA~initial pore spacing}~\label{fig:p2p_45}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_50.png}\quad	
			\vspace{-1.25em}
			\caption{50 \AA~initial pore spacing}~\label{fig:p2p_50}
		\end{subfigure}
		\begin{subfigure}{0.3\textwidth}
			\includegraphics[width=\textwidth]{p2p_55.png}
			\vspace{-1.25em}
			\caption{55 \AA~initial pore spacing}~\label{fig:p2p_55}
		\end{subfigure}

@@

		\item 5 \AA~: We tested a pore radius of 5 \AA~because it is
		slightly larger than the equilibrated pore radius of the system simulated with
		an intial pore radius of 2.5 \AA. After being run through the full dry
		equilibration procedure, the average pore radius is 0.42 $\pm$ 0.01 \AA, which
		agrees with the 2.5 \AA~configuration within uncertainty.

@@

	  \begin{figure}[!htb]
	  \centering
          \includegraphics[width=\textwidth]{slit_pores.png}
	  \caption{A system that was built with an initial pore radius of 8
		  \AA~equilibrates to a structure that exhibits both cylindrical and slit-like
		  pores. As pictured here, sodium ions are colored blue, carbon atoms in the
		  aromatic ring of the head group are colored orange and all else is colored
		  cyan.}~\label{fig:slits}
	  \end{figure}

@@

	  We tested 3 different initial layer spacings, defined as the distance
	  between the planes of aromatic rings in each layer. Systems built with layers
	  stacked 3.7 \AA~and 5 \AA~apart are discussed extensively in the main text. We
	  also tested a system built with layers stacked 10 \AA~ apart.

@@

	  \begin{figure}[!htb]
		\centering
		\includegraphics[width=0.5\textwidth]{dbwl_10.png}
		\caption{When layers are initially stacked 10 \AA~apart and the system
                is equilibrated using the dry equlibration procedure, large vacuum gaps
		form as the monomers attempt to fill space.}\label{fig:dbwl_10} 
	  \end{figure}

@@

%  \noindent
%  \begingroup
%        \fontsize{14pt}{14pt}\selectfont
%	\textbf{Calculation of pore-to-pore spacing statistics}
%  \endgroup

  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.25\textwidth]{p2p_diagram.png}
	\caption{There are five pore-to-pore distances that are equal in a perfect
		hexagon. If each number in the diagram represents the center of a
		pore in a hexagonal unit cell, then the distance from 1 to 2, 2 to 4, 
		4 to 3, 3 to 1 and 1 to 4 should be equal. Only 4 of the distances
		are independent. For example, the distance from 1 to 4 is defined by
		the location of all other pore centers.}
	\label{fig:p2p_diagram}
  \end{figure}

  \section{The nematic order parameter}\label{method:nematic_order}

  We calculated the nematic order parameter for our system in order to
  understand the degree of ordering among monomer head groups. Typically, the
  nematic order parameter is calculated for nematic liquid crystal systems which
  are characterized by unidirectional ordering of liquid crystal monomers. The
  preferred direction of monomers is defined by the unit director vector,
  $\mathbf{n}$. Assuming a single preferred direction of alignment, the nematic
  order parameter, $S$, is defined as:
  \begin{equation}
	 S = \frac{1}{2} \langle(3\cos^2\theta -1)\rangle
	\label{eqn:nematic_order_parameter}
  \end{equation}
  where $\theta$ is the angle between the molecular long axis and $\mathbf{n}$.
  In a perfectly ordered nematic liquid crystal system, the molecular axis of each
  monomer should be aligned with $\mathbf{n}$ and give an order parameter of $S=1$. 
  We are interested in quantifying the degree of monomer head group alignment 
  between systems. We use Eq.~\ref{eqn:nematic_order_parameter} to accomplish this
  by defining $\mathbf{n}$ as the z-axis (or pore axis), and then measuring the angles,
  $\theta$, between $\mathbf{n}$ and the vectors perpendicular to the plane of
  the aromatic head groups ($\mathbf{v}$ in Figure~\ref{fig:director}).

  %BJC: change n to v in picture.
  \begin{figure}[!htb]
	\centering
	\includegraphics[width=0.75\linewidth]{nematic_director.png}
	\caption{We calculate the nematic order parameter by measuring the angle
	between $\mathbf{v}$ and the z-axis.}~\label{fig:director}
  \end{figure}

  The nematic order parameter is highest in sandwiched systems. 
  Figure~\ref{fig:nematic_distribution} shows the distribution of angles between
  the nematic director and the vector perpendicular to the monomer head groups. 
  Systems in the ordered basin have higher nematic order parameters than their
  disordered basin counterparts. Both sandwiched system have higher nematic order
  parameters than both parallel displaced systems. This may occur because monomers
  in the sandwiched configuration have their motion restricted by vertically adjacent
  monomers, while those in the parallel displaced configuration have more room to 
  rotate.

  \begin{figure}[!htb]

  \section{Measurement of intensities of experimental and simulated XRD patterns}\label{section:xrd_intensities}

  We developed standardized methods of measuring the intensity of reflections of interest
  in the experimental and simulated X-ray diffraction patterns presented in this work. Here,
  we graphically illustrate the methods used for measuring these intensities.

  All diffraction patterns are normalized according to R-alkanes and the intensities
  of all reflections are reported relative to the intensity of R-alkanes. The region
  used to calculate the average intensity of R-alkanes is shown in 
  Figure~\ref{fig:ralkanes}. The top region is excluded because, in the simulated
  patterns, R-$\pi$ intersects with R-alkanes.

  R-$\pi$ and R-double are reported as the maximum values of the peaks of the 
  $q_z$ cross-section of the experimental pattern at $q_r=0$ (Figure~\ref{fig:rpi_rdouble}).
  In the case of the experimental pattern, the peak heights are not symmetrical,
  so we report the average of the two heights.

  We measured R-spots by calculating the average intensity within a region 
  selected by visual inspection. We report the average intensity within the regions 
  highlighted in red in Figure~\ref{fig:rspots}. If there are no easily discernable
  spots, we report the average intensity at the intersection of R-alkanes with
  the $q_z$ value of R-double since that is where we expect it to appear based on
  experiment. Since R-double does not appear in our simulated patterns, we 
  estimate where it should appear as half of the $q_z$ value of R-$\pi$.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{WAXS_raw.png}
  \caption{Unaltered experimental WAXS pattern}\label{fig:unaltered}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{ralkanes.png}
  \caption{R-alkanes}\label{fig:ralkanes}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rpi_rdouble.png}
  \caption{$q_z|_{r=0}$}\label{fig:rpi_rdouble}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{rspots.png}
  \caption{R-spots}\label{fig:rspots}
  \end{subfigure}
  \caption{}\label{fig:xrd_intensities}
  \end{figure}

  \section{Noise in simulated diffraction patterns}\label{section:xrd_noise}

  The magnitude of noise in the simulated diffraction patterns decrease as 
  the number of independent configurations increases. We simulated the structure
  factor of 100 randomly placed particles and varied the number of independent 
  configurations (N). It is expected that the structure factor should resemble
  a two-dimsional gaussian. We cannot sample enough independent configurations
  of our system to completely eliminate noise.

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{xrd_1frame.png}
  \caption{N=1}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{xrd_10frame.png}
  \caption{N=10}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{xrd_100frame.png}
  \caption{N=100}
  \end{subfigure}
  \begin{subfigure}{0.45\linewidth}
  \centering
  \includegraphics[width=\textwidth]{xrd_10000frame.png}
  \caption{N=10000}
  \end{subfigure}
  \caption{The magnitude of noise, especially along $q_r$=0, decreases
  as the number of independent configurations (N) increases.}\label{fig:xrd_noise}
  \end{figure}

@@

  \vspace{1em}
  Experimentalists did not measure the correlation length, so we estimated it
  from the raw data. We took a slice of the 2D WAXS data along the dashed line in
  Figure ~\ref{fig:waxs_dashed}. We removed background noise by subtracting the
  intensity far from the pattern (high $q$) uniformly. We used a least squares
  algorithm to fit a lorentzian curve to the data. Only values recorded above
  $q_z$ = 1.6 were considered for the fit in order to mitigate interference from
  R-alkanes (Figure~\ref{fig:correlation_length_exp}). The full width at half
  maximum (FWHM) is related to the correlation length, L, by the relationship: $
  L = \frac{1}{FWHM} $. The error in the value is calculated as the square root
  of the diagonal entry of the covariance matrix of optimized fit paramaters.
  We estimate the value of the correlation length to be 10 $\pm$ 1 using this 
  method. Since the experimental peak width is also influenced by strain and 
  instrumental broadening in addition to finite size broadening, the value 
  calculated here is really only an upper bound on the correlation length. 
  % need citations and more on lorentzian parameters
  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.45\textwidth}	
  	\includegraphics[width=\textwidth]{waxs_dashed.png}
	\caption{}~\label{fig:waxs_dashed}
  \end{subfigure}
  \begin{subfigure}{0.45\textwidth}
	\includegraphics[width=\textwidth]{Correlation_length_exp.png}
	\caption{}~\label{fig:correlation_length_exp}
  \end{subfigure}
  \caption{(a) We estimated the system's experimental correlation length using a 
  1D slice of the 2D WAXS patterns along $q_r$=0. (b) We fit a lorentzian curve 
  to the 1D slice. One of the fit parameters is the full width at half maximum (FWHM).
  The correlation length is 1/FWHM.}~\label{fig:correlation}
  \end{figure}
  \vspace{1em} \\

  \begin{figure}[!htb]
  \centering
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{offset_density.png}
        \caption{Parallel Displaced, Ordered Pore Basin}
        \label{fig:offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{layered_density.png}
        \caption{Sandwiched, Ordered Pore Basin}
        \label{fig:layered_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_offset_density.png}
        \caption{Parallel Displaced, Disorderd Pore Basin}
        \label{fig:disordered_offset_density}
  \end{subfigure}
  \begin{subfigure}{0.47\textwidth}
        \includegraphics[width=1\linewidth]{disordered_density.png}
        \caption{Sandwiched, Disordered Pore Basin}
        \label{fig:disorder_layered_density}
  \end{subfigure}
  \caption{In all cases, the component radial distribution functions exhibit a
	  composition gradient transitioning from the hydrophilic to the hydrophobic
	  regions. Systems with layers initially spaced 3.7 \AA~apart in the  parallel
	  displaced (a), and sandwiched (b) configurations both show the highest
	  concentrations of ions and head groups away from the pore center. Systems with
	  layers initially spaced 5 \AA~apart (c) and (d), both show the highest
	  concentrations of ions and head groups near the pore center, implying a more
	  uniform, disordered pore.}~\label{fig:densities}
  \end{figure}
